---
title: 'Practice 5.1 (Ming Pei, Li : 61143008S)'
author: "Ming Pei Li"
date: "2024-11-03"
output: html_document
---

```{r setup, message = FALSE}
library(rgbif)
library(leaflet)
library(dplyr)
```

### Download occurrence data for Alexandromys kikuchii
```{r}
gbif_voles <- occ_search(
  scientificName = "Alexandromys kikuchii",
  hasCoordinate = TRUE,
  basisOfRecord = 'HUMAN_OBSERVATION',
  limit = 1000)
```

### Extract the data frame 
```{r}
gbif_voles <- gbif_voles$data %>%
  filter(!is.na(decimalLongitude) & !is.na(decimalLatitude)) %>%
  select(decimalLongitude, decimalLatitude)
```

`!is.na(decimalLongitude) & !is.na(decimalLatitude)` ensures that "longitude and latitude are not NA (missing values)". 
`select()` is used to choose the columns we need.

### Create map 
```{r}
Ak <- leaflet (data = gbif_voles) %>%
  addTiles() %>%   # Add the base map layer
  addCircleMarkers(
    lng = ~decimalLongitude, 
    lat = ~decimalLatitude,
    color = "brown", 
    radius = 5) %>%
  setView (lng = 120.96, lat = 23.6, zoom = 7)%>%
  addControl(html = "<strong> Distribution of Alexandromys kikuchii </strong>", position = "topright")

Ak
```


`addTiles()` is used to add the base map layer
`lng = ~decimalLongitude` and `lat = ~decimalLatitude` set the coordinates for each marker.

`setView()`:
1. Sets the initial view and zoom level of the map.
2. `lng = 120.96` and `lat = 23.6` center the map at Taiwan's coordinates.
3. sets zoom = 7, suitable for observing the Taiwan area.

`addControl()` is used to add custom HTML titles or text to the map.
The html parameter accepts HTML formatted text, such as <strong> for bold text.
"<strong>Distribution of Alexandromys kikuchii</strong>": Closes the </strong> tag to make the entire title text bold.
